\documentclass[../../main.tex]{subfiles}
 
\begin{document}
\label{sec:teaching}

In this chapter, I reflect upon my teaching experiences, and analyze the results of course evaluations.  I submitted a supplementary PEGP on teaching in Fall 2019.  In that report, I included all courses I taught up to January Term, 2019.  For this report, I continue from January 2019 through the present.  I am excited to share with you many positive student outcomes from a diverse set of courses.  In Sec. \ref{sec:teaching_philosophy}, I have followed the FPC recommendation to reflect upon the role of physics courses within the broader liberal arts curriculum.  Given the goals of Whittier College, and persistent divisions within our broader culture, I felt called to reflect in Sec. \ref{sec:equity_inclusion} on specific ways I put the values of equity and inclusion into practice in my courses.
\\
\vspace{0.25cm}
In my report submitted in Fall 2019, I discussed a variety of physics teaching modules based in Physics Education Research (PER) and traditional styles.  In Sec. \ref{sec:methods}, I review and categorize these methods and highlight which ones I use.  I also discuss laboratory activities and online modules in Sec. \ref{sec:methods}.  In Secs. \ref{sec:intro} and \ref{sec:intro_eval}, I describe my introductory physics and math courses, and the corresponding evaluations.  In Secs. \ref{sec:adv} and \ref{sec:adv_eval}, I reflect in the same way for advanced courses.  Sections \ref{sec:lib} and \ref{sec:lib_eval} follow the same pattern, but for my \textit{CON2} and \textit{CUL3} courses.  Sections \ref{sec:writing} and \ref{sec:writing_eval} contain descriptions and analysis for INTD100, my section of college writing seminar.  Finally, in Sec. \ref{sec:outlook} I give my outlook on future teaching.

\section{Teaching Philosophy: Growth, Order, and Shared Meaning}
\label{sec:teaching_philosophy}

%\begin{flushleft}
%\subfile{teaching_philosophy/teaching_philosophy}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/teaching_philosophy/teaching_philosophy}
\end{flushleft}

\section{Addressing Equity and Inclusion}
\label{sec:equity_inclusion}

%\begin{flushleft}
%\subfile{equity_inclusion/equity_inclusion}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/equity_inclusion/equity_inclusion}
\end{flushleft}

\section{Methods of Teaching Physics}
\label{sec:methods}

%\begin{flushleft}
%\subfile{methods/methods}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/methods/methods}
\end{flushleft}

\section{Introductory Course Descriptions}
\label{sec:intro}

%\begin{flushleft}
%\subfile{intro_course_desc/intro_course_desc}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/intro_course_desc/intro_course_desc}
\end{flushleft}

\section{Analysis of Course Evaluations: Introductory Courses}
\label{sec:intro_eval}

%\begin{flushleft}
%\subfile{intro_course_desc_eval/intro_course_desc_eval}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/intro_course_desc_eval/intro_course_desc_eval}
\end{flushleft}

\section{Advanced Course Descriptions}
\label{sec:adv}

%\begin{flushleft}
%\subfile{adv_course_desc/adv_course_desc}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/adv_course_desc/adv_course_desc}
\end{flushleft}

\section{Analysis of Course Evaluations: Advanced Courses}
\label{sec:adv_eval}

%\begin{flushleft}
%\subfile{adv_course_desc_eval/adv_course_desc_eval}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/adv_course_desc_eval/adv_course_desc_eval}
\end{flushleft}

\section{Liberal Arts Course Descriptions}
\label{sec:lib}

%\begin{flushleft}
%\subfile{lib_course_desc/lib_course_desc}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/lib_course_desc/lib_course_desc}
\end{flushleft}

\section{Analysis of Course Evaluations: Liberal Arts Courses}
\label{sec:lib_eval}
%\begin{flushleft}
%\subfile{lib_course_desc_eval/lib_course_desc_eval}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/lib_course_desc_eval/lib_course_desc_eval}
\end{flushleft}

\section{College Writing Seminar Course Descriptions}
\label{sec:writing}

%\begin{flushleft}
%\subfile{lib_course_desc/lib_course_desc}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/college_writing_desc/college_writing_desc}
\end{flushleft}

\section{Analysis of Course Evaluations: College Writing Seminar}
\label{sec:writing_eval}

%\begin{flushleft}
%\subfile{lib_course_desc_eval/lib_course_desc_eval}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/college_writing_desc_eval/college_writing_desc_eval}
\end{flushleft}

\section{Outlook}
\label{sec:outlook}

%\begin{flushleft}
%\subfile{outlook/outlook}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/teaching/outlook/outlook}
\end{flushleft}

\end{document}
