\documentclass[../../main.tex]{subfiles}
 
\begin{document}
\label{sec:advising_mentoring}

I reflect on my role as an advisor and mentor at Whittier College below.  I have mentored both first-year students, before they select their department and major, and majors in the STEM area.  In Sec. \ref{sec:adv_teaching}, I reflect on the connection between advising and teaching.  In Sec. \ref{sec:first_year}, I reflect on mentoring and welcoming first-year students to Whittier College.  In Sec. \ref{sec:adv_stem}, I review my experiences guiding Physics, ICS, and 3-2 engineering majors to graduation.  Finally, in Sec. \ref{sec:adv_wsp}, I reflect on my experience guiding a student to graduate through the Whittier Scholars Program.

\section{Connections to Teaching}
\label{sec:adv_teaching}

%\begin{flushleft}
%\subfile{teaching/teaching}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/advising_mentoring/teaching/teaching}
\end{flushleft}

\section{Advising and Mentoring First Year Students}
\label{sec:first_year}

%\begin{flushleft}
%\subfile{first_year/first_year}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/advising_mentoring/first_year/first_year}
\end{flushleft}

\section{Advising and Mentoring Majors in Physics, ICS, and 3-2 Engineering}
\label{sec:adv_stem}

%\begin{flushleft}
%\subfile{majors/majors}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/advising_mentoring/majors/majors}
\end{flushleft}

\section{Advising and Mentoring Whittier Scholars Program Majors}
\label{sec:adv_wsp}

%\begin{flushleft}
%\subfile{wsp/wsp}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/advising_mentoring/wsp/wsp}
\end{flushleft}

\end{document}
