\documentclass[../../main.tex]{subfiles}
 
\begin{document}

Since January 2019, I have taught introductory and advanced STEM courses in a variety of disciplines.  I have also created and taught brand new liberal arts courses in exploration and history of science.  I stepped forward to volunteer for College Writing Seminar, and gained wonderful advisees in the process.  Having reflected on my teaching practices, I find that my students are regularly succeeding, despite learning in a difficult period.  Algebra-based physics continues to be the most challenging course to teach, but my students in general are learning well.  I have discovered that I can teach courses beyond the traditional STEM area, and I will continue to serve that part of the curriculum.  Though teaching College Writing Seminar was a stretch for me, the students responded well, and now a subset of them are in my STEM courses this semester.  I look forward to observing their writing skills.
\\
\vspace{0.25cm}
Perhaps the last piece of the puzzle in my teaching portfolio corresponds to the more advanced physics courses.  This is not to say that I should sacrifice my liberal arts courses or writing course in order to teach advanced physics courses.  I only remark that I should teach, at some point, courses like experimental physics lab, quantum mechanics, computational physics, and statistical physics.  This would ensure that I know how to teach them well, as my colleagues do, so I could step forward to teach them should the need arise.  I am very grateful to my colleagues for their continued support and feedback.

\end{document}
