\documentclass[../../main.tex]{subfiles}
 
\begin{document}
\label{sec:service}

A key part of our mission as professors is to share in the governance of our institution.  In this chapter, I reflect on how I have done my very best to help Whittier College function.  I have realized, as part of this reflection, that I have a strong desire to participate in the Whittier Scholars Program.  This realization came about also as part of my advising practice (see Ch. \ref{sec:advising_mentoring}).  In Sec. \ref{sec:committee_service}, I discuss committee work achieved from 2018 to the current semester.  In Sec. \ref{sec:first_year}, I discuss my involvement with First Year Orientation.  In Sec. \ref{sec:oer_workshops}, I describe workshops I helped to give on Open Educational Resources (OER) in collaboration with Wardman Library.  Finally, in Sec. \ref{sec:cec_artemis}, I reflect on a service I performed for the local Whittier Community.

\section{Committee Service}

%\begin{flushleft}
%\subfile{committee/committee}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/service/committee/committee}
\end{flushleft}

\section{First Year Orientation}

%\begin{flushleft}
%\subfile{orientation/orientation}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/service/orientation/orientation}
\end{flushleft}

\section{Open Educational Resources (OER) Workshops}

%\begin{flushleft}
%\subfile{oer_workshops/oer_workshops}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/service/oer_workshops/oer_workshops}
\end{flushleft}

\section{Center for Engagement with Communities: The Artemis Program}
\label{sec:cec2}

%\begin{flushleft}
%\subfile{cec_artemis/cec_artemis}
%\end{flushleft}

\begin{flushleft}
\subfile{sections/service/cec_artemis/cec_artemis}
\end{flushleft}

\end{document}
