\documentclass[../../../main.tex]{subfiles}
 
\begin{document}

The liberal education courses I have taught thus far at Whittier College are now introduced, with connections to the teaching philosophy described in Sec. \ref{sec:methods}.

\subsubsection{Safe Return Doubtful: History and Current Status of Modern Science in Antarctica}

In 1913, an advertisement appeared in a London newspaper that read ``Men wanted for hazardous journey, small wages, bitter cold, long months of complete darkness, constant danger, \textbf{safe return doubtful}, honor and recognition in case of success. - Ernest Shackleton, 4 Burlington St.''  Ernest Shackleton, who was to set several records in Antarctic exploration in the early 20th century, was calling for volunteers for the first expedition to cross Antarctica ocean-to-ocean.  There is a wonderfully rugged and inspiring batch of historical accounts of the modern exploration of Antarctica, from first landing to the triumphant arrival of humans to the South Pole for the first time.  This literature is included within the broader category of \textit{exploration literature.}
\\
\vspace{0.25cm}
I have been to Antarctica twice.  I recall that people who succeed on missions there share something in common, even though they are as diverse a group as any: they know themselves.  They understand their goals and their personal limitations.  People who travel to McMurdo Station, United States Antarctic Program (USAP) are scientists and engineers, explorers, pilots, mechanics, medics, and workers who help the base function.  They do not mind being uncomfortable, as long as they know they are serving the right purpose.  They work \textit{hard,} often for little recognition.  They train thoroughly, but can also improvise and survive.  My aim for our students is to encountered traits like these, and learned to incorporate them in their studies through \textit{shared meaning} (see Sec. \ref{sec:teaching_philosophy}).
\\
\vspace{0.25cm}
To that end, I have created INTD255: \textit{Safe Return Doubtful: History and Current Status of Modern Science in Antarctica}, a \textit{CON2}-style course.  We include three main themes. First, we cover the race to be the first humans to arrive at the South Pole in 1911.  Second, we cover current scientific projects in Antarctica.  Third, we write weekly journal entries that invite the students to look inside and see their potential for true exploration.  Themes like inclusion arise as we learn that the first group to the South Pole took indigenous science seriously.  Led by the same captain who completed the Northwest Passage, this group incorporated methods of travel and survival from indigenous people in Northern Canada.  We build \textit{order} and \textit{shared meaning} (Sec. \ref{sec:teaching_philosophy}) between topics like physics, chemistry, biology, history, and indigenous technology.  The students learn about scientific results and endeavors currentlty active in Antarctica, and historically.  Examples of journal activities invite students to describe a time they were in a dangerous situation and how they handled it, or a time they were called to lead.  I chose to conclude the course with a lecture on leadership \cite{west_point}.
\\
\vspace{0.25cm}
Much like my physics courses, I include active learning strategies to keep the students engaged with the science modules.  One example was an activity in which the students accessed ice-core data from a NOAA database and graphed measured oxygen isotope ratios from trapped air bubbles.  This is how we estimate global average temperatures over hundreds of thousands of years.  In another example, the students planned a navigation from Ross Island (the location of McMurdo Base, USAP) to the Central Trans-Antarctic Mountains that lead to the South Pole.  The exercise requires students to plan how they would move both themselves and their food, assuming people and pack animals consume a certain number of calories per day.  These activities connect environmental and biological science with historical exploration.  Students must pay attention to detail in order to not starve or get lost.  Eventually, we applied the navigational technique of triangulation on a group hike to the summit of Hellman Park.  The students use a compass and the baseline between SLC and the summit in Hellman Park to calculate the distance to Downtown Los Angeles\footnote{Though we had a wide range of math preparation in the class, as a group we got the right answer to within 6\%, according to Google Maps.}.  Finally, I include lecture content about Antarctic wildlife, neutrino physics (see Sec. \ref{sec:scholarship}), and climate science.
\\
\vspace{0.25cm}
For reading, we tackle ``The Last Place on Earth'' by Roland Huntford.  Like an expedition, I plan out the students' trek through this book, and we complete short weekly reading quizzes to keep everyone accountable.  The book is an expansive history of polar exploration, and I wish \textit{every single one} of the physicists in my field would read it for the contrasting examples of leadership styles.  The author paints portraits of the Norwegian Roald Amundsen, who led the first group to the South Pole, and Englishman Robert Falcon Scott, who arrived second but died on the return journey.  We see them planning years in advance, and failing on purpose just to learn what works.  We see scientists assuming their navigational calculations are correct, only to find out in the field they missed something and pay dearly.  We see explorers learning to eat strange food and move across terrain in ways used by indigenous Canadians.  An example: everyone trying to explore Antarctica kept developing scurvy.  Captain Scott and the British canned limes but the Vitamin C was rendered less potent in shipment.  Captain Amundsen noticed that the \textit{Netsilik} tribe never developed scurvy, despite having no access to fruit like the British, or berries like the Scandanavians.  Where is the nutrition above the Arctic Circle?  The answer is under the sea, so the Netsilik eat things that bring the vitamins from the sea: seals.  The Norwegians did not bother bringing limes or lingenberries, but instead ate seal meat in Antarctica.
\\
\vspace{0.25cm}
We also include the wonderful writings of Barry Lopez from ``Horizon.''\footnote{Rest in peace, December 2020.}  One chapter deals with his travels to the side of Antarctica explored originally by Shackleton, Scott, and Amundsen.  Lopez describes the daily lives of scientists in Antarctica by chronicling a mission to retrieve meteorites from the outer solar system that land on the ice sheets.  In another chapter, Lopez describes riding south on a large ice-breaking research vessel to the side of Antarctica nearer to the Southern tip of Latin America.  Lopez writes about the life of indigenous people in that area, and the effect the land has on culture.  We also include ``News at the Ends of the Earth'' by Hester Blum, which is a collection of essays regarding the writings and printed work of the polar explorers.  It turns out that some polar explorers transported whole printing presses to Antarctica in order to create shipboard newspapers and other scientific chronicles.  The writing deals with topics like a changing climate, and the possibility of no remaining places on Earth unexplored.  I am grateful to Profs. Michelle Chihara and Warren Hansen for suggesting these books as helpful additions.  Prof. Hansen audited my course, and we enjoyed discussing the reading together.

\subsubsection{A History of Science in Latin America}

As I shared in Sec. \ref{sec:intro}, I was inspired by my family and our students to create a new course entitled \textit{A History of Science in Latin America}.  The course was assigned a \textit{Culture 3} and \textit{Connections 2} designation.  Twenty-six students took this course in Spring 2021 (module 1).  The high enrollment was due in part to the \textit{CON2} and \textit{CUL3} designations.  I observed that the students' selection of final project topics often involved the country of origin of their ancestors or historical anecdotes from their families.  Thus, I drew the conclusion that the students were hungry for a course that covered science in Latin America.  I had been thinking over the course idea since 2017-18, but finally got the chance in Spring 2021 to offer it.
\\
\vspace{0.25cm}
One aspect of the course students encounter first are the ideas of scientific communities, and which are central or peripheral communities. Taking STEM courses alone might lead a student to believe that European and American cities have been central to scientific progress, and that Latin American communities have been peripheral. Peripheral, in this sense, refers to a community that merely adopts discoveries from the central ones and rarely produces progress. By honestly covering the colonial period in Latin America, we found examples in which Latin American communities were central and their European counterparts were peripheral. A more accurate description of scientific progress for Latin America and Europe would be a full two-way exchange of knowledge.
\\
\vspace{0.25cm}
For example, two cures for syphilis were brought back to Europe by Spanish colonials: chinaberry bark and sarsaparilla root.  Even Spanish sources acknowledge that these treatments (which exploded commercially starting in the 1600s) were revealed to the colonials by indigenous doctors.  There is a similar story behind quinine production from \textit{cinchona} bark to treat malaria.  Spanish colonials would have been operating from the medical theory of the \textit{four humours,} and the Mexica and other Nahua peoples had a wholly separate spiritual and scientific worldview that involved the human body.  No matter which was more correct, the people who produced a working treatment were simply those who had the data from the native plant.
\\
\vspace{0.25cm}
The students also encountered the idea that mathematical and scientific systems developed all over Latin America in the pre-Columbian era.  We learned to translate numbers from our system of Arabic numerals to Mayan, Incan, and Aztec systems.  This required the students to learn a piece of a branch of mathematics called number theory.  The students then were able to perform calculations regarding land use and agriculture using the numerical systems of the era\footnote{A sample assignment is included in the supporting material.}.  We branched into the mathematics and the astronomy of the solar system, because the 1600s-1700s saw rapid development in this branch of science worldwide.  Universities founded by Jesuits and Dominicans in what are now Columbia, Per\'{u}, and Venezuela held interesting debates about the structure of the solar system.  Meanwhile, the construction of Latin American technical colleges was underway and funded primarily by the very mineral extraction (for example, silver) the viceroyalties valued so highly.  Often, native mining techniques were shown to be more efficient than those imported from Europe.  As the Scientific Revolution spread through Mex\'{i}co, Columbia, Per\'{u}, and R\'{i}o de La Plata, several fascinating examples of science performed by indigenous citizens emerged.
\\
\vspace{0.25cm}
Thus, the students absorb a more complex and complete picture of the Scientific Revolution that demonstrates both Latin Americans and Europeans working towards the truth. Mexican scientists participated in the first measurements of the distance to the Sun using Venus transits.  By timing the transit of Venus across the face of the Sun, and comparing times from opposite sides of the planet, the distance to the Sun can be derived.  Measurements from Europe alone would have been insufficient.  Teams were dispatched from Britain and France to Russia, Tahiti, and Baja California.  Mexican scientists, rather than European visitors, completed the Baja measurements and the data helped establish the correct (and astonishing) value to within a few percent error.  Some of the same Mexican scientists found and explained the connection between sunspots and the aurora borealis.  The answer has to do with the cosmic rays in the solar wind (Sec. \ref{sec:scholarship}) and the magnetic fields of the Earth and Sun.  This discovery was based on data from a Northern aurora that flared as far South as Mexico City and Zacatecas.  One Mexican scientist even recreated the aurora light \textit{in the lab} using charged particles striking gas.  Some European scientists adopted a theory that the aurora originated at the North Pole from inside the Earth.  Humans would not reach the North Pole for more than one hundred years.
\\
\vspace{0.25cm}
Through our activities, the students absorb a more complex and complete picture of the Scientific Revolution that demonstrates both Latin Americans and Europeans working towards the truth.  The students perform activities asynchronously and engage in some group work.  Since it had to be taught online, I asked the students how much time we should spend in breakout rooms.  They told me that less time spent in breakout rooms was preferable.  I also created videos and activity worksheets for the students to complete.  Supplemented by our excellent reading, \textit{Science in Latin America, A History}, edited by Juan Jos\'{e} Salda\~{n}a, we proceeded from the 1500s up to 1900.  This book appears to be one of only a few histories of Latin American science written in the last 10 years.  As long as I provide context from physics, mathematics, and chemistry, the students seemed to follow it.  We would have liked to go further, but we were restricted due to the seven week limitation of the module system.  For final project design, I contacted Sonia Chaidez from Wardman Library to introduce Digital Storytelling to our students.  The students learned to use WeVideo, a web-based video editing tool.  Whittier College has a site license, so this was free for our students.  The students performed brilliantly, and we learned about everything from silver mining in Mexico to cosmic rays and Mayan mathematics.

\end{document}
