\documentclass[../main.tex]{subfiles}
 
\begin{document}

This semester marks the beginning of my fifth year with Whittier College.  These years have been filled with both wonderfully uplifting experiences, but also sacrifice.  I hope that my writing and analysis in Sec. \ref{sec:teaching} have shown that my teaching practice is thriving.  Despite the rapid transition to online instruction, and the module system, my students and I have demonstrated increased success in learning.  The written responses provided valuable insight into \textit{why} certain practices work.  It is my prediction that the students will continue to favor projects and project-based learning over assessments like midterms and finals.  This is a trend I noticed throughout last year.  I have taken seriously the FPC call to broaden my educational horizons by expanding my liberal arts portfolio.  I successfully created two new liberal arts courses that deal with cross-cultural issues within historical and current scientific progress.  I have also taught college writing seminar (INTD100), and I can return to it periodically.
\\
\vspace{0.15cm}
Our research program continues to grow.  The beginning of our membership as an IceCube Collaboration institution will provide a new avenue of physics scholarship for our students.  We are excited to resume participation in the development of the world's largest neutrino detector in the quest for UHE-$\nu$.  Our brand new collaboration with the Office of Naval Research (ONR) will help our students participate in engineering research.  Our students are eagerly signing up, and as of this writing, I am helping them to polish resum\'{e}s for application to ONR programs.  The ONR has given me an alternative route to performing quality research in the pandemic-induced pause experienced in the UHE-$\nu$ field.  There is also an interesting synergy between my physics and ONR engineering research: phased-array radar development.  The new research area of CEM will benefit our students' education and our long-term research goals.
\\
\vspace{0.15cm}
I finally had the opportunity to discuss my committee service.  Having served on ESAC, ERC/DLAC, and now EPC, I have received broad experience in how Whittier College operates.  With ESAC, we found a way to set admissions criteria that reflected our genuine desire to admit students we can support, and help to thrive.  Our proposal was ultimately adopted by the faculty after many negotiations and much data analysis.  I am proud of our our committee came together to address a difficult issue, and incorporated feedback from all sides.  With ERC, we found ways to help students archive their work so that their achievements are preserved long after they graduate.  I keep returning, however, to my experience with WSP.  It seems like a natural fit, and I hope to join the WSP Advisory board when it is practical.  For this semester, I will serve on EPC after a request from the Faculty Chair.
\\
\vspace{0.15cm}
I have had wonderful experiences with all of my new advisees, both majors and non-majors.  Though I began advising before the pandemic, the experiences that stand out recently are my dogged attempts to create a sense of belonging for students that were blocked from coming to campus for the first time in Fall 2020.  One of my brand new advisees is on the football team, and I finally can see him for the first time in my algebra-based physics class.  Another of mine is in Computer Logic and Digital Circuit Design.  I am helping her to apply for the ONR research program, and she joins a very excited cohort of computer science physics students who are now taking that course.  As part of our departmental assessment procedures, I learned that I do a relatively large amount of advising to first-year and second-year students.  I will periodically return to the First-Year Orientation and adopting a new cohort of first-year advisees.  For now, however, my plate appears to be full.
\\
\vspace{0.15cm}
I want to thank all members of the Faculty Personnel Committee for their hard work this year.  I realize that my report is longer than most.  There are many pieces of my work for Whittier College about which I have not had the opportunity to share with you until now.  I anticipate that my report next year will be far more succinct.  From my family to yours, we hope you are all healthy and well.
\\
\vspace{0.15cm}
Respectfully submitted,
Jordan C. Hanson
\end{document}
